\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-03 paper.tex
5. Moved conclusion to end, after evidence. Oops!

\subsubsection{``Public Good'' By The Numbers}
In order to argue that the public good is being upheld I assert that Utilitarianism is the most effective ethical system to use because it judges actions based on the net happiness of everyone. Utilitarianism is ``[t]he creed which ... holds that actions are right in proportion as they tend to promote happiness, wrong as they tend to produce the reverse of happiness.'' \cite{Utilitarianism} A utilitarian view in this case would be that World of Warcraft does not create addiction in the majority of the world and therefore does not diminish mental or physical welfare of the public.

The most shocking statistic I found came from Dr. Maressa Orzack, founder and coordinator of Computer Addiction Services \cite{CompAddictionServices}, who cites that up to 40\% of World of Warcraft players could be addicted. \cite{FortyPercentAddicted} If everyone in the world played World of Warcraft, a total of over 7 billion people \cite{WorldPopulation}, and Dr. Ozark's prediction is correct, 2.8 billion people would be addicted. Based purely on the numbers that leaves 60\% of the world's population that is not addicted.

>>>>

\subsubsection{``Public Good'' By The Numbers}
In order to argue that the public good is being upheld I assert that Utilitarianism is the most effective ethical system to use because it judges actions based on the net happiness of everyone. Utilitarianism is ``[t]he creed which ... holds that actions are right in proportion as they tend to promote happiness, wrong as they tend to produce the reverse of happiness.'' \cite{Utilitarianism}

The most shocking statistic I found came from Dr. Maressa Orzack, founder and coordinator of Computer Addiction Services \cite{CompAddictionServices}, who cites that up to 40\% of World of Warcraft players could be addicted. \cite{FortyPercentAddicted} If everyone in the world played World of Warcraft, a total of over 7 billion people \cite{WorldPopulation}, and Dr. Ozark's prediction is correct, 2.8 billion people would be addicted. Based purely on the numbers that leaves 60\% of the world's population that is not addicted. A utilitarian view in this case would be that World of Warcraft does not create addiction in the majority of the world and therefore does not diminish mental or physical welfare of the public.
